Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-06-01 manuscript.Rmd
Update interpretations for target-only WCRQA

### Syria as Target
The time period of differing dynamics---from observation 38 through 
43---appears to be captured by the RR and DET values in
WCRQA of social cohesion and count of negative
events (Figure \@ref(fig:plot-wcrqa-targ-all)). The
amount of recurrence and determinism for these periods almost consistently
lie above chance, suggesting that the intensity of negative events coincide
with the degree of social cohesion found on Twitter and that these 
shared trajectories extend across multiple days.

The above-chance levels of determinism and recurrence rate demonstrate
the coupling of social cohesion to both total and negative events during
times of strife. During this period, 
the modal ICEWS event for each day (Figure \@ref(fig:plot-mode-event))
during May 1st--15th was almost consistently -10, the most violent 
event category. These dates directly correlate with the above-chance RR and DET
metrics for the WCRQA of social cohesion and count of negative events.
Furthermore, for WCRQA of social cohesion and positive event count during
this time period, DET was entirely within chance (Figure
\@ref(fig:plot-wcrqa-targ-all)). This supports our hypothesis, as the
positive events are seemingly not coupled with the social cohesion on Twitter
during civil uprisings during the Arab Spring.

>>>>

### Syria as Target
The time period of differing dynamics noted in the cross-recurrence
plots---from observation 32 through 47---appears to be captured 
by the above-chance RR values in WCRQA of social cohesion and count of all
events (Figure \@ref(fig:plot-wcrqa-targ-all)). However,
DET for these periods only intermittently
rises above chance; it more consistently reaches statistical
significance only at the end of the window through the end of the observation
period, following a spike in the RR between
negative event count and social cohesion. 
During this period, 
the modal ICEWS event for each day (Figure \@ref(fig:plot-mode-event))
was almost consistently -10, the most violent 
event category. This supports our first hypothesis.

Surprisingly---and contrary to our second hypothesis---we saw consistent
coupling between positive event count and social cohesion. Although
both had a downward trajectory throughout the time period under consideration,
RR was at or above chance in nearly all windows, and DET showed
much more consistent shared trajectories than negative events.
This may suggest that Syrian Twitter community was reacting more cohesively
to the positive events aimed at Syria from the international community;
this interpretation is supported by the attenuation of the effect in the
analyses that include Syria as both a source and a target.
